\section*{Report Requirements}


This is a brief overview of the requirements on the \coursename{} and some guidelines for the report.


\subsection*{Deliverables}

You are expected to hand-in the following items on ADAM until \textbf{Tuesday, 28th January 2020 23:59}:

\begin{itemize}
    \item This \textbf{report}, as PDF and the complete sources of your report in the same structure as distributed as a ZIP archive
    \item A 30 second to 1 minute \textbf{video}, showcasing your project and its capabilities
    \item Your \textbf{slides} for the final presentation on January, 30 2020. You will have max. 15 minutes to present your project (you are allowed to use less than the full 15 minutes) and there will be 5-10 minutes of Q\&A following your presentation
\end{itemize}

\subsection*{Structure}

The sections in this template are already a guideline for the structure of your report.
You are allowed to change the titles. However, please make sure that the content outlined below is included in your report.

\begin{description}
    \item[Introduction]  Why is your topic important / interesting (how is it related to the topic of the seminar / existing research projects), what specific goal(s) did your project have and how did you implement them. The introduction should give a brief and relevant overview of the topic and your project and already indicate to the reader the results of your project.
    \item[Concepts] Describe and justify theoretical concepts / technologies used and reference / discuss / summarize relevant literature here. Show and discuss the architecture of your project.
    \item[Implementation] Briefly summarize your implementation work. You may also show / discuss the architecture in this section, depending on your project and what you deem appropriate.
    \item[Usage] A manual for users and developers of your project: How do you set it up, how is it used?
    \item[Conclusion] Briefly summarize the outcomes of your project, lessons learned and make recommendations for future work (both smaller improvements to your specific project and bigger ideas) 
\end{description}

\subsection*{Deadline}

The deadline for the hand-in is on \textbf{Tuesday, 28th January 2020 23:59}.\\
Please hand-in all the required files in the corresponding form on ADAM.


\vspace*{1em}
\noindent 
On the next page, there is a guide on how to use this template. Please read it carefully and stick to it. We will compile a document with all reports together and distribute that to all participants.

\clearpage
\pagebreak